Hybrid platforms and bargaining power

### 2023-12-16 src/paper/application.tex
Add figure for extension - total welfare

\pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-0.3.csv}\equilibriumFullSurplusOneSided
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.5_lambda-1.csv}\equilibriumFullSurplusOneSided
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1_lambda-1.csv}\equilibriumFullSurplusTwoSided

@@

With this proven, we can rely on \cref{prop:aggregate_size_additive} to see that, in equilibrium, an increase in $N_P$ decreases $N_F$.
Furthermore, this decrease is so large that total product variety, and thus total surplus (which in turn is equal to total profits) also decreases.\footnote{
    As long as the market is in the hybrid regime.
    If $N_F^* = 0$, then an increase in $N_P$ mechanically increases total aggregate, and thus total surplus.
}
Thus, as in the case without consumer entry fees, a platform becoming increasingly hybrid has generally negative consequences.

>>>>

\pgfplotstableread[col sep=comma]{out/figures/equilibrium.csv}\equilibrium
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_profit_onesided_scale-1_lambda-1.csv}\equilibriumProfitOneSided
\pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_onesided_scale-0.6_lambda-1.csv}\equilibriumFullSurplusOneSided
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1_lambda-1.csv}\equilibriumFullSurplusTwoSided
% \pgfplotstableread[col sep=comma]{out/figures/equilibrium_welfare_twosided_scale-1_lambda-0.5.csv}\equilibriumProfitOneSidedLowLambda

@@

With this proven, we can rely on \cref{prop:aggregate_size_additive} to see that, in equilibrium, an increase in $N_P$ decreases $N_F$.
Furthermore, this decrease is so large that total product variety, and thus total surplus (which in turn is equal to total profits) also decreases.\footnote{
    As long as the market is in the hybrid regime.
    If $N_F^* = 0$, then an increase in $N_P$ mechanically increases total aggregate, and thus total surplus.
}
\Cref{fig:equilibrium_full_surplus_one_sided} displays equilibrium outcomes for an example parametrization
Thus, as in the case without consumer entry fees, a platform becoming increasingly hybrid has generally negative consequences.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                    xlabel={$N_P$},
                    ylabel={},
                    xmin=0, xmax=1.5, % adjust these values as needed
                    ymin=0, ymax=3.1, % adjust these values as needed
                    axis lines=left,
                    xtick=\empty, ytick=\empty,
                    legend pos=south east,
                    width=\textwidth,
                ]
                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=N_P]{\equilibriumFullSurplusOneSided};
                \addplot[color=myred,mark=none,thick] table[x=N_P,y=N_F]{\equilibriumFullSurplusOneSided};
                \addplot[color=black,mark=none,thick,dashed] table[x=N_P,y=A]{\equilibriumFullSurplusOneSided};

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];

                \legend{$N_P$, $N_F$, $A$}
            \end{axis}
        \end{tikzpicture}
        \caption{Platform product variety and number of fringe entrants}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                    xlabel={$N_P$},
                    ylabel={},
                    xmin=0, xmax=1.5, % adjust these values as needed
                    ymin=0, ymax=1.2, % adjust these values as needed
                    axis lines=left,
                    xtick=\empty, ytick=\empty,
                    legend pos=north west,
                    width=\textwidth,
                ]
                \addplot[color=myblue,mark=none,thick] table[x=N_P,y=pi_P]{\equilibriumFullSurplusOneSided};
                \addplot[color=myred,mark=none,thick] table[x=N_P,y=pi_F]{\equilibriumFullSurplusOneSided};

                \addplot[draw=none,name path=hybrid] table[x=N_P,y=hybrid]{\equilibriumFullSurplusOneSided};
                \addplot[draw=none,name path=bottom] {0};
                \addplot [fill=black, fill opacity=0.05] fill between [of=hybrid and bottom];

                \legend{$\pi_P(N_P)$, $\pi_F(N_P)$}
            \end{axis}
        \end{tikzpicture}
        \caption{Platform and fringe profits}
    \end{subfigure}
    \caption{Equilibrium outcomes in the case when the whole surplus is bargained over ($N_C = 0.6, V_P = 1, V_F = 1, I_F = 0.2$). As in the case of bargaining over profits, the platform's profits are increasing in $N_P$, while the fringe's profits are decreasing. Consumer surplus does not matter in this case, as it is extracted by the platform. The shaded region represents hybrid operation, while in the unshaded region, the platform operates in pure retail mode.}
    \label{fig:equilibrium_full_surplus_one_sided}
\end{figure}
